### 2022-09-29 inst/Examples/Paper_results/Paper_results_2.Rmd
Fixed bug in tiepointsimmer
Issue arose from adding tie-point-parameter specification

We then estimate the dating uncertainty for all 29 events
```{r}
agesimmatrix_d18O = matrix(NA,29,nsims)
depthlist_d18O = c()
do.plot.rampfit = TRUE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,4,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,4,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")

@@

```{r}

>>>>

We then estimate the dating uncertainty for all 29 events
```{r compare_transitions_1}
agesimmatrix_d18O = matrix(NA,29,nsims)
depthlist_d18O = c()
do.plot.rampfit = TRUE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,4,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,4,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")

@@

```{r compare_transitions_2}
